---
title: "Progress Memo 2"
subtitle: |
  | Final Project 
  | Data Science 1 with R (STAT 301-1)
author: "Catherine Johnston"
pagetitle: "PM2 Catherine Johnston"
date: "November 20, 2024"

format:
  html:
    toc: true
    toc-depth: 4
    toc-location: left
    embed-resources: true
    link-external-newwindow: true

execute:
  warning: false

from: markdown+emoji
reference-location: margin
citation-location: margin
---

::: {.callout-tip icon="false"}
## Github Repo Link

[Catherine's GitHub Repo (ccjohnston1)](https://github.com/ccjohnston1/final-project-1.git)
:::


```{r}
#| label: package-load
#| echo: false

#load packages
library(tidyverse)

#dataset load 
movie_data <- read_csv(file = "data/movies_metadata.csv")

```

# Cleaning data
```{r}
#| label: clean-up
#| echo: false

#getting rid of NA rating rows & renaming vote to rating
clean_movie_data <- movie_data |>
  filter(!is.na(vote_average) & !is.na(vote_count)) |>
  rename(average_rating = vote_average, 
         rating_count = vote_count)

#omitting duplicate rows
clean_movie_data <- unique(clean_movie_data)

#parsing strings from spoken languages
#clean_movie_data <- clean_movie_data |>
  
  
  
```



## Exploratory Data Analysis 1
```{r}
#| label: eda-1
#| echo: false
  
#clean_movie_data |> 
  #mutate(average_rating, case_when(
    #average_rating =< 4.9 ~ "Low Rating",
    #average_rating == 5 ~ "Average Rating",
    #average_rating =< 10 ~ "High Rating"
 # )
    
 # )

```
Checking for a correlation between movie run times and ratings

## Exploratory Data Analysis 2
```{r}
#| label: eda-2
#| echo: false

```
Checking for a correlation between movie run times and ratings


## Exploratory Data Analysis 3
```{r}
#| label: eda-3
#| echo: false


```
Checking for a correlation between movie run times and ratings

## Exploratory Data Analysis 4
```{r}
#| label: eda-4
#| echo: false


```
Checking for a correlation between languages and rating count

## Exploratory Data Analysis 5
```{r}
#| label: eda-5
#| echo: false


```
Checking for a correlation between ratings and popularity.

## Summary

As demonstrated by the above EDA, I want to look into how different aspects of movies (or the creation of movies) affect ratings.
