---
title: "Progress Memo 1"
subtitle: |
  | Final Project 
  | Data Science 1 with R (STAT 301-1)
author: "Catherine Johnston"
pagetitle: "PM1 Catherine Johnston"
date: "November 3, 2024"

format:
  html:
    toc: true
    toc-depth: 4
    toc-location: left
    embed-resources: true
    link-external-newwindow: true

execute:
  warning: false

from: markdown+emoji
reference-location: margin
citation-location: margin
---

::: {.callout-important collapse=true}
## Memo format

Like all other submissions for this course, we expect the memo to be **neat and well organized**.

A memo is a short, polished report. Meaning, it should be well written and thoughtfully laid out. Some neatness and organizational hints/tips (not an exhaustive list):

- There should be absolutely no code in your report --- don’t hide it; code should not be visible/accessible.
- Include a date indicating when report was created.
- There should be no tibbles/data frames or raw R output --- should use tables (avoid unnecessarily long output)!
- Any plots or graphics should be polished (appropriate labels and/or captions).
- All figures and tables should be properly labeled and referenced --- must make use of quarto cross-referencing.
- Should use heading and sub-headings appropriately.
- Remove prompts and instructions meant to assist students.
- Should include a link to project’s GitHub repo.
- GitHub repo should be well organized and have a few commits (no templates, commit of most recent work)


:::

::: {.callout-warning collapse=true}
GitHub (free account) cannot store large files. If you try to commit and push a large dataset you will have an ERROR! Any file over 100 MB (100,000 KB) needs to be added to the `.gitignore` file BEFORE committing.

**We may need to do that for files in your final project!**
:::


::: {.callout-tip icon=false}

## Github Repo Link

[Catherine's GitHub Repo](https://github.com/ccjohnston1/final-project-1.git)

:::

## Package load
```{r}
#| label: package-load
#| code-fold: TRUE

library(tidyverse)
```


## Data source

```{r}
#| label: data-source-load
#| code-fold: TRUE

movies_data <- read.csv(file = "data/movies_metadata.csv")
```

Movies dataset^[https://www.kaggle.com/datasets/rounakbanik/the-movies-dataset?select=movies_metadata.csv. Accessed Nov 3, 2024]

This dataset contains 24 variables and 45,466 observations. It takes a look at films released on or before July of 2017 and lists certain aspects of the film, like its original language, where it was filmed, average ratings, budget, revenue, etc. Average ratings of the movies listed are on a scale from 1-5, and were obtained from the official GroupLens website. There are 26 million individual ratings from 270,000 users for all 45,000 movies that have been averaged out for each film. This dataset is a collaboration of a bunch of smaller datasets, all examining different aspects of the 45,000 movies. All 6 smaller datasets have been combined together to create the dataset I am using for this project. 


## Why this data

Blah blah blah^[another footnote]

## Data quality & complexity check

```{r}

```


## Potential data issues

Blah blah blah

## Misc

Blah Blah
